A fast algorithm for computing best response strategies in two-person sequential games

### 2014-07-26 paper.tex
more
new bib file (for game theory citing)

\begin{document}
\onecolumn
\title{A fast algorithm for computing best response strategies in two-person sequential games}

@@

\subsection{Statement of the problem}
Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
as opposed to simultaneous play.} in \textit{sequential-form} (See for example, page 2 of \cite{koller-1995},
for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
We will be referring to the other player as ``the opponent''. We are interested in the problem of
finding a best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$, given a fixed
(possibly mixed) strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose entries are $-1$, $0$, or $+1$,
and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$ and $e$ encode linear constraints on our ``admissible''
realization plans\footnote{In games in sequential form, the terms ``strategy'' and ``realization plan''
mean thesame thing.} $x$, in the sequential form representation of the game.
In the language of convex-optimization,
one can readily give the following saddle-point formulation for this problem. Viz,

@@

A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against the opponent's fixed strategy $y_0$.

@@

In section II, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
We elaborate our proposed algorithm in section III.

\section{Related work}
Pending...

@@

\subsection{Primal-dual gap stopping-criterion and convergence of the algorithm}
Pending...

@@

% ==========
% = biblio =
% ==========
% {\small
\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv}
\end{document}

>>>>

\begin{document}
%\onecolumn
\title{A fast algorithm for computing best response strategies in two-person sequential games}

@@

\subsection{Statement of the problem}
Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
as opposed to simultaneous play.} in \textit{sequential-form} (See for example, \cite{von1996efficient} and \cite{koller1996efficient} 
for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
We will be referring to the other player as ``the opponent''. We are interested in the problem of
finding a best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$, given a fixed
(possibly mixed) strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose entries are $-1$, $0$, or $+1$,
and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$ and $e$ encode linear constraints on our ``admissible''
realization plans\footnote{In games in sequential form, the terms ``strategy'' and ``realization plan''
mean thesame thing.} $x$, in the sequential form representation of the game.
In the language of convex-optimization,
one can readily give the following saddle-point formulation for this problem. Viz,

@@

\begin{definition}
A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against the opponent's fixed strategy $y_0$.
\end{definition}

@@

In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
We elaborate our proposed algorithm in section \ref{sec:algo}.

\section{Related work}
\label{sec:related_work}

Pending...

@@

\subsection{Convergence of the algorithm and practical stopping-criteria}
Pending...

@@

% ==========
% = biblio =
% ==========
% {\small
\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv.bib,agt.bib}
\end{document}
